\documentclass[a4paper,twocolumn,12pt]{article}
\usepackage{url}

\title{I2P: An anonymous overlay network}

\author{Mikal Villa}

\begin{document}
\maketitle

\begin{abstract}\noindent
This paper will present I2P, a scalable, self organizing, resilient packet
switched anonymous network layer, upon which any number of different
anonymity or security conscious applications can operate. Each of these
applications may make their own anonymity, latency, and throughput tradeoffs
without worrying about the proper implementation of a free route mixnet,
allowing them to blend their activity with the larger anonymity set of users
already running on top of I2P.
\end{abstract}

\tableofcontents

\section{High level overview}
I2P is not an academic, commercial, nor governmental research project. It is 
instead an engineering effort aimed at designing a protocol to provide a 
sufficient level of anonymity to those who need it. Despite not being an 
official research project, analysis of the network's design is encouraged for 
the purposes of providing better security.

I2P is designed to allow peers using I2P to communicate with each other
anonymously --- both sender and recipient are unidentifiable to each other
as well as to third parties. Having the ability to run services within I2P
is essential, as it is quite likely that any outbound proxies to the normal
Internet will be monitored, disabled, or even taken over to attempt more
malicious attacks.

The network itself is message oriented --- it is essentially a secure and anonymous
IP layer, where messages are addressed to cryptographic keys (Destinations) and can
be significantly larger than IP packets. Some example uses of the network include
``eepsites'' (webservers hosting normal web applications within I2P), a BitTorrent\cite{cohen08specification}
client (``I2PSnark''), or a distributed data store.

To deal with a wide range of attacks, I2P is fully distributed with no centralized
resources --- and hence there are no directory servers keeping statistics regarding
the performance and reliability of routers within the network. As such, each router
must keep and maintain profiles of various routers and is responsible for selecting
appropriate peers to meet the anonymity, performance, and reliability needs of the users.

The network itself makes use of a significant number of cryptographic techniques and
algorithms --- a full laundry list includes 2048bit ElGamal\cite{DBLP:journals/tit/Elgamal85}
encryption, 256bit AES\cite{books/sp/DaemenR02} in CBC mode with PKCS\#5 padding, 1024bit 
DSA\cite{2000--dss} signatures, SHA256 hashes, 2048bit Diffie-Hellman negotiated connections with 
station to station authentication, and ElGamal / AES+SessionTag.

\vspace{2 em}

With the help of the I2PTunnel application, a user are able to stream
traditional TCP/IP\cite{rfc793} applications over I2P. Most people will not use I2P
directly, or even need to know they're using it.

Note that while there have been several simple SOCKS proxies available to tie
existing applications into the network, their value has been limited as nearly
every application routinely exposes what, in an anonymous context, is sensitive
information. The only safe way to go is to fully audit an application to ensure
proper operation and to assist in that we provide a series of APIs in various
languages which can be used to make the most out of the network.

\section{Destinations}

On the regular internet, clients and servers are identified by IP addresses\cite{}.
I2P has an equivalent anonymous identifier called a Destination. A single I2P
router can host any number of Destinations; generally each individual client
app or service will have its own Destination. Crucially, a Destination is not
directly linked in any way to the I2P router's IP address. The unlinkability
is provided by using tunnels (see Section \ref{sec:tunnels}).

Destinations are a datastructure consisting of a public encryption key, a
public signing key and a ``certificate'' (a container for various receipts or
proof-of-works). The current implementation uses a 256-byte public key plus a
128-byte signing key plus (by default) a null certificate, for a total of 387
bytes. Destinations are generally displayed and used in modified\footnote{I2P
uses a filesystem- and URL-friendly set of characters, replacing $/$ with
$\sim$, and $+$ with $-$} Base64\cite{rfc4648} representation, which for the
current implementation gives a 516-byte string.

In addition to a single I2P router hosting multiple Destinations, it is possible
for multiple routers to host the same Destination. This is a technique known as
``multihoming'', and is commonly used to prevent uptime monitoring attacks\cite{}
or to provide service failovers.

\section{Booting into the network}

When starting the I2P router for the first time it will select a random port to use for UDP\cite{rfc768}
and TCP connections to other routers, then continue with requesting ``RouterInfo'' files
from randomly selected ``reseed servers'' maintained by voluenteers to start communicating
with the first I2P routers. The reseed process is done over HTTP or HTTPS. The router will prefer
UDP connections for faster transmission of packages.

\section{Network database}

The Network database (``netDb'') is used to keep track of peer and service
information. The ``RouterInfo'' representent a data structure holding data for a
given peer, this includes IP, port and public keys. It also keep track of
service information, which is known as ``LeaseSets''. The Network database is a
distributed hash table based on the Kademlia\cite{Maymounkov:2002:KPI:646334.687801} protocol.

\subsection{LeaseSets}

The LeaseSets contain information about the service, as the public key and
tunnel endpoints that can be contacted to reach the service. A tunnel is set to
expire after ten minutes and the LeaseSet with the old service information is
useless after the tunnels expire. LeaseSets need to be sent anonymously, to avoid
correlating a router with its LeaseSets.

\subsection{Floodfill}

The floodfill servers works as database servers distributed in the hash table,
this is a decentralized solution while on the other hand Tor\cite{tor-design}
uses a centralized directory server system.

\section{Tunnels} \label{sec:tunnels}

Tunnels are part of the core of I2P, and it's formed by a gateway, a set of
participants and an endpoint. Two types of tunnels exist, ``outbound'' tunnels
send messages away from the tunnel creator, while ``inbound'' tunnels bring
messages to the tunnel creator.
Layered encryption is used, so each of the routers can only decrypt a single
layer. The decrypted information contains the IP of the next router, along with
the encrypted information to be forwarded.

\subsection{Tunnel creation}
The tunnel's creator selects exactly which peers will participate in the tunnel,
and provides each with the necessary configuration data. Each local client destination
has its own set of inbound tunnels and outbound tunnels of any number in parallel.
They may also have any number of hops. This can be configured to meet its anonymity and
performance needs per destination. It is the intent to make it hard for either participants or
third parties to determine the length of a tunnel, or even for colluding participants
to determine whether they are a part of the same tunnel at all (barring the situation
where colluding peers are next to each other in the tunnel). The router does the job itself
to maintain a series of pools for participating in the network database and for managing the
tunnels themselves. It also got certain rules that don't allow IPs from the same /19 network to
participate in the same tunnel sets.

\subsection{Tunnel connections}
Combining these two tunnels allows users to send messages to each other. The
sender router sets up an outbound tunnel, while the receiver router creates an
inbound tunnel. The gateway of an inbound tunnel can receive messages from any
other user and will send them on until the endpoint. The endpoint of the
outbound tunnel will need to send the message on to the gateway of the inbound
tunnel. To do this, the sender adds instructions to its encrypted message. Once
the endpoint of the outbound tunnel decrypts the message, it will have
instructions to forward the message to the correct inbound gateway.

Outside of the core I2P layer, there is an optional end to
end streaming library available for client applications, exposing TCP-esque operation,
including message reordering, retransmission, congestion control, etc.

\section{Naming}

\subsection{Base32 Names}

I2P supports Base32\cite{rfc4648} hostnames similar to Tor's\cite{tor-design} .onion
addresses. Base32 addresses are much shorter and easier to handle than the full
516-character Base64 Destinations or addresshelpers. Example:
ukeu3k5oycgaauneqgtnvselmt4yemvoil
kln7jpvamvfx7dnkdq.b32.i2p

In Tor\cite{tor-design}, the address is 16 characters (80 bits), or half of the
SHA-1 hash.  \cite{tor-hiddenservice} I2P uses 52 characters (256 bits) to
represent the full SHA-256 hash. The form is {52 chars}.b32.i2p.
Tor\cite{tor-design} has recently published a proposal to convert to an
identical format of {52 chars}.onion for their hidden services. Base32 is
implemented in the naming service, which queries the router over I2CP to lookup
the LeaseSet to get the full Destination. Base32 lookups will only be
successful when the Destination is up and publishing a LeaseSet. Because
resolution may require a network database lookup, it may take significantly
longer than a local address book lookup.

Base32 addresses can be used in most places where hostnames or full
destinations are used, however there are some exceptions where they may fail if
the name does not immediately resolve. I2PTunnel will fail, for example, if the
name does not resolve to a destination.

\subsection{Naming service}

I2P ships with a generic library and base implementation designed to work off a
name to destination mapping. An addon called the addressbook is also included,
which works as a web-of-trust, distributed, human readable naming system.
The router will request new names from entries in the addressbook known as
subscriptions, these works like DNS servers works on the internet.
If an application (I2PTunnel or the HTTP\cite{http-rfc} proxy) wishes to access a destination
by name, the router does a very simple local lookup to resolve that name.


\section{Conclution}


\bibliographystyle{plain}
\bibliography{references}

\end{document}
